%-------------------------
% Resume in Latex
% Author : Raman Shinde
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \textbf{#1}}
  }

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubhead}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeCase}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}


\newcommand{\resumePoint}[1]{\item\small{{#1}\vspace{-4pt}}}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\newcommand{\resumeSubPointS}{\begin{itemize}\vspace{4pt}}
\newcommand{\resumeSubPointE}{\end{itemize}\vspace{-4pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/raman-shinde-562950b2}{\Large Raman Shinde}} & Email : \href{mailto:raman.shinde15@gmail.com}{raman.shinde15@gmail.com}\\
  \href{https://github.com/Raman-Raje}{https://github.com/Raman-Raje} & Mobile : +91 9595161238 \\
\end{tabular*}


%%---------Career Objective--------------
%\section{Career Objective}
%Results-oriented professional with clo years of experience in python development and expertise in Machine-learning, Deep Learning,Computer Vision and Natural Language Processing (NLP).

%----------Career Summary---------------
\section{Career Summary}
\resumeSubHeadingListStart
    \resumePoint{Senior Lead Engineer specializing in AI inference, compute, and performance optimization for Deep Learning and LLMs, with strong expertise in TVM, MLC-LLM, and Llama.cpp.}
    
    \resumePoint{Enhanced neural network performance by optimizing code generation, operator schedules, and runtimes specifically for edge and mobile devices.}
	
	\resumePoint{Expertise in developing Deep Learning architectures including Transformers, LLMs, CNNs, and LSTMs, bridging the gap between model design and hardware execution.}
	
	\resumePoint{Proficient in scalable ML deployments using AWS, GCP, Docker, and Kubernetes, backed by a strong foundation in classical ML algorithms (Random Forest, SVM, GBDT).}

\resumeSubHeadingListEnd  

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Qualcomm}{Banglore, India}
      {Senior Lead Engineer [AI Research]}{Mar. 2024 - Present}
      \resumeItemListStart
        	\resumeSubPointS
        		\item Implemented texture support support for OpenCL and Vulkan backends in TVM, optimizing data access patterns on Adreno GPUs to achieve a \textbf{50\%} reduction in inference time.
        		\item Extended TVM by adding support for new operators, layers and runtime features, enabling deployment of LLMs and Diffusion models on edge hardware.
                \item Integrated CLML acceleration into the GGML and llama.cpp frameworks, bypassing generic compute paths to deliver hardware-optimized performance for on-device inference.
        	\resumeSubPointE
          
      \resumeItemListEnd    
  
  \resumeSubheading
      {Imagination Technologies}{Pune, India}
      {Deep Learning Engineer}{Sep. 2021 - Mar. 2024}
      \resumeItemListStart
        	\resumeSubPointS
        		\item Developed an SDK enabling neural network execution on GPUs and NNAs using TVM, simplifying and accelerating model deployment on edge devices.
        		\item Implemented LSTM/RNN support in the Neural Compute SDK for PyTorch, TensorFlow and ONNX, ensuring broader compatibility and accelerated performance.
        		\item Optimized RelayIR by developing custom graph transforms, improving execution efficiency across diverse workloads.
        		\item Contributed to the development of quantization tools (static, dynamic, and QAT) for multiple frameworks, enhancing model compression and boosting inference speed.
        	\resumeSubPointE
          
      \resumeItemListEnd  
  
  \resumeSubheading
      {Xpanxion}{Pune, India}
      {Data Scientist}{Jan. 2020 - Sep. 2021}
      \resumeItemListStart
        	\resumeSubPointS
        		\item Developed AI/ML solutions to extract information from medical documents, including document classification and candidate extraction (e.g., benefits, rates, and drug details) using libraries like Fonduer, Tesseract, and OpenCV.
        		\item Built reusable AI/ML components within the Innovation Team, including a content-based and collaborative recommendation system, NLP modules such as Named Entity Recognition (NER), Q&A systems, and sequence translation.
        		\item Led Computer Vision projects involving object localization and detection, image segmentation, and gesture recognition.
        	\resumeSubPointE
          
      \resumeItemListEnd

    \resumeSubheading
      {Siemens R\&D}{Pune, India}
      {Product Development Engineer}{Dec. 2018 - Dec 2019}
      \resumeItemListStart
        	\resumeSubPointS
        		\item Developed and enhanced an application for designing manufacturing sequences, with significant contributions to debugging and resolving issues in existing code.
        		\item Accelerated feature deployment by implementing new use-cases and Proof-of-Concepts (POCs), enabling faster shipping of key features.
				
        	\resumeSubPointE
 
      \resumeItemListEnd

    \resumeSubheading
      {TCS}{Pune, India}
      {Software Developer}{Dec 2015 - Nov 2018}
      \resumeItemListStart
			\resumeSubPointS
        		\item Developed monitoring and control applications for NCRA, including real-time issue monitoring, debugging, and GUI modifications based on client requirements.
        		\item Provided support for financial applications such as CRD and SRD for Morgan Stanley, ensuring reliable performance and issue resolution.
				\item Built applications for various clients using Python and C++, contributing to diverse projects and delivering tailored software solutions.
			
        	\resumeSubPointE         
                 
      \resumeItemListEnd
	  
  \resumeSubHeadingListEnd

 %--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages:}{Python, C++}
    \resumeSubItem{Database:}{MySql, MongoDB}
    \resumeSubItem{Data Analysis:}{Pandas, Numpy, Matplotlib, Seaborn, openCV}
    \resumeSubItem{ML/DL Toolkit:}{Keras, scikit-learn , tensorflow, pytorch, TVM}
  \resumeSubHeadingListEnd 

%--------CERTIFICATION------------

\section{Certifications/Internship}
 \resumeSubHeadingListStart
 	\resumePoint{Applied Machine Learning course at Applied AI. ( Jan 2018 to May 2019)}
 	\resumePoint{Completed Standford Statistical Learning (Self-Paced) course.}
 	\resumePoint{Completed Deep Learning Specialization course from Coursera}
 	\resumePoint{Internship at IARE, Aurangabad on Industrial automation. (May 2014 - Jun 2014)}
 	
 \resumeSubHeadingListEnd
   
%--------ACADEMICS------------

\section{Education}
  \resumeSubHeadingListStart
    \resumePoint{\textbf{B.Tech} in Electronics and Telecommunication from SGGSIE\&T, Nanded with \textbf{CGPA 7.7} (2011 - 2015)}
    \resumePoint{Class Xll (HSC), form Maharashtra State Board of Education with \textbf{83.33\%} (2009 - 2011)}
     \resumePoint{Class X (SSC), form Maharashtra State Board of Education with \textbf{90.92\%}  (2008 - 2009)}
  \resumeSubHeadingListEnd  
  

\end{document}
