%-------------------------
% Resume in Latex
% Author : Raman Shinde
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \textbf{#1}}
  }

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubhead}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeCase}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}


\newcommand{\resumePoint}[1]{\item\small{{#1}\vspace{-4pt}}}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\newcommand{\resumeSubPointS}{\begin{itemize}\vspace{4pt}}
\newcommand{\resumeSubPointE}{\end{itemize}\vspace{-4pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Raman Shinde} \\ \vspace{5pt}
    \small 
    \href{mailto:raman.shinde15@gmail.com}{\underline{raman.shinde15@gmail.com}} $|$ 
    +91 9595161238 $|$ 
    \href{https://www.linkedin.com/in/raman-shinde-562950b2}{\underline{LinkedIn}} $|$ 
    \href{https://github.com/Raman-Raje}{\underline{GitHub}}
\end{center}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Qualcomm}{Banglore, India}
      {Senior Lead Engineer [AI Research]}{Mar. 2024 - Present}
      \resumeItemListStart
            \resumeSubPointS
                \item Implemented texture support support for OpenCL and Vulkan backends in TVM, optimizing data access patterns on Adreno GPUs to achieve a \textbf{50\%} reduction in inference time.
                \item Extended TVM by adding support for new operators, layers and runtime features, enabling deployment of LLMs and Diffusion models on edge hardware.
                \item Integrated CLML acceleration into the GGML and llama.cpp frameworks, bypassing generic compute paths to deliver hardware-optimized performance for on-device inference.
            \resumeSubPointE
          
      \resumeItemListEnd    
  
  \resumeSubheading
      {Imagination Technologies}{Pune, India}
      {Deep Learning Engineer}{Sep. 2021 - Mar. 2024}
      \resumeItemListStart
            \resumeSubPointS
                \item Developed an SDK enabling neural network execution on GPUs and NNAs using TVM, simplifying and accelerating model deployment on edge devices.
                \item Optimized RelayIR by developing custom graph transforms, improving execution efficiency across diverse workloads.
                \item Contributed to the development of quantization tools (static, dynamic, and QAT) for multiple frameworks, enhancing model compression and boosting inference speed.
            \resumeSubPointE
          
      \resumeItemListEnd  
  
  \resumeSubheading
      {Xpanxion}{Pune, India}
      {Data Scientist}{Jan. 2020 - Sep. 2021}
      \resumeItemListStart
            \resumeSubPointS
                \item Developed AI/ML solutions to extract information from medical documents, including document classification and candidate extraction (e.g., benefits, rates, and drug details).
                \item Built reusable AI/ML components within the Innovation Team, including a content-based and collaborative recommendation system, NLP modules such as Named Entity Recognition (NER), Q&A systems, and sequence translation.
                \item Led Computer Vision projects involving object localization and detection, image segmentation, and gesture recognition.
            \resumeSubPointE
          
      \resumeItemListEnd

    \resumeSubheading
      {Siemens R\&D}{Pune, India}
      {Product Development Engineer}{Dec. 2018 - Dec 2019}
      \resumeItemListStart
            \resumeSubPointS
                \item Developed and enhanced an application for designing manufacturing sequences, with significant contributions to debugging and resolving issues in existing code.
                \item Accelerated feature deployment by implementing new use-cases and Proof-of-Concepts (POCs), enabling faster shipping of key features.
            \resumeSubPointE
 
      \resumeItemListEnd

    \resumeSubheading
      {TCS}{Pune, India}
      {Software Developer}{Dec 2015 - Nov 2018}
      \resumeItemListStart
            \resumeSubPointS
                \item Developed monitoring and control applications for NCRA, including real-time issue monitoring, debugging, and GUI modifications based on client requirements.
                \item Provided support for financial applications such as CRD and SRD for Morgan Stanley, ensuring reliable performance and issue resolution.   
            \resumeSubPointE         
                 
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

 %--------TECHNICAL SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
     \resumeSubItem{Languages/Frameworks}{: Python, C++, C, PyTorch, TensorFlow}
     \resumeSubItem{Cloud/Deployment}{: AWS, GCP, Docker, Kubernetes, Git}
 \resumeSubHeadingListEnd 

%--------ACADEMICS------------
\section{Education}
  \vspace{2pt}
  \textbf{B.Tech in Electronics and Telecommunication}, SGGSIE\&T, Nanded with \textbf{CGPA 7.7} (2011 - 2015)
\end{document}